Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-22 paper.tex
rm a todo
progress on section 4

@@

\subsection{\effCEK{C} is equivalent to \ineffCEKD, provided $C$ is an instance of the Lazy D ADT}
\label{secc:framework:monoid-correct}

In this subsection, we prove that for all $C$, if $C$ is a Lazy D Cast
ADT, then
\[
  \evalEqv{\effCEK{C}}{\ineffCEKD}
\]

The main work of proof is in a lemma that establishes a weak
bisimulation between \ineffCEKD{} and \effCEK{C}.  The bisimulation
goes more smoothly if we require two more properties of the cast
representation: that the casts form a monoid (the $id$ and $seq$
operators) and that the cast constructor is equivalent to the identity
operator when applied to an identical source and target type.

\todo[inline]{UNDER CONSTRUCTION -JS}

We prove that if a instance of Cast ADT $C$ is
Lazy D and is a monoid, then $eval_\mathcal{D} =
eval_{\mathcal{S}(C)}$. We proof this theorem with a weak bisimulation
between \effCEK{C} and \ineffCEKD.

Some instances of Cast ADT (or "some Cast" for short) are also 
\textit{monoids}. This definition is useful in the proof of 
our framework.

\begin{definition}[Monoid]
	A Cast is a monoid if 
	for all
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c_1) = c_1$,
		\item $seq(c_1,id(T_2)) = c_1$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{definition}

@@

\todo[inline]{In Fig.~\ref{fig:bisim-SC-D}, how to suppress rule numbers like 
	(1), (2), etc.? -KC}
Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation. Here we omit rules 
that make the relation a congruence.
%
The relation $\kappa \approx \kappa$ relates two continuations. 
%
If $k \approx \kappa$, adding an identity cast on top of $k$ gives a related 
continuation. 
%
If $\kappa_1 \approx \kappa_2$, extending $\kappa_1$ and $\kappa_2$ with the 
same cast gives related results.
%
%
The relation $v \approx v : T$ relates two value and also report their type. We 
will see shortly why reporting the type. 
%
If two values of type $P$ are related, injecting them to $\TOOdyn$ gives 
related values.
%
Unit values are of course related.
%
To relate to a non-casted function in \ineffCEKD, the function in \effCEK{C} 
must use identities as its casts.
%
If functions are related, we can apply the same cast on both side.
%
Rules for products and sums are similar.

@@

\begin{figure}
	$\text{\effCEK{C}} \approx \text{\ineffCEKD}$
	\[\dots\]

	\fbox{$\kappa \approx \kappa$}
	\begin{gather*}
	\inference{
		k \approx \kappa
	}{
		wrap(k) \approx \kappa
	}
	\quad
	\inference{
		\kappa_1 \approx \kappa_2
	}{
		ext(cast(T_1,l,T_2),\kappa_1) \approx 
		\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_2}
	}
\\
	\end{gather*}
\\	
	\fbox{$v \approx v : T$}
	\begin{gather}
	\inference{
		v_1 \approx v_2 : P
	}{
		\hcvOOinj{P}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
		: \TOOdyn
	}
\\ \\
	\inference{}{
		\hcvOOtt \approx \vOOtt : \POOunit
	}
	\quad
	\inference{}{
		\hcvOOtt \approx \vOOcast{\vOOtt}{\cOOcast{\POOunit}{l}{\POOunit}}
		: \POOunit
	}
	\\ \\
	\inference{
		\rho_1 \approx \rho_2 &
		dom(\rho_1) = dom(\rho_2) = \Gamma \\
		\Gamma , x : T_1 \vdash e : T_2
	}{
		\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)}
		\approx
		\vOOfun{\rho_2}{x}{e}
		: \POOfun{T_1}{T_2}
	}
\\ \\
\inference{
\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v_2 : \POOfun{T_1}{T_2} \\
%		\judgeType{\hcvOOfun{c_1}{\rho}{x}{e}{c_2}}{\POOfun{T_1}{T_2}} \\
c_1' = seq(cast(T_3,l,T_1),c_1) \\
c_2' = seq(c_2,cast(T_2,l,T_4))
}{
\hcvOOfun{c_1'}{\rho}{x}{e}{c_2'}
\approx
\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}}
: \POOfun{T_3}{T_4}
}
\\ \\
	\inference{
		v_1 \approx v_2 : T_1 &
		v_3 \approx v_4 : T_2 &
	}{
		\hcvOOcons{v_1}{id(T_1)}{v_3}{id(T_2)}
		\approx
		\vOOcons{v_2}{v_3}
		: \POOprod{T_1}{T_2}
	}
\\ \\
	\inference{
		\hcvOOcons{v_1}{c_1}{v_3}{c_2} \approx v_2 : \POOsum{T_1}{T_2} \\
		c_1' = seq(c_1,cast(T_1,l,T_3)) \\
		c_2' = seq(c_2,cast(T_2,l,T_4))
	}{
		\hcvOOcons{v_1}{c_1'}{v_3}{c_2'} \approx
		\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{\POOprod{T_3}{T_4}}}
		: \POOprod{T_3}{T_4}
	}
\\ \\
	\inference{
		v_1 \approx v_2 : T_1
	}{
		\hcvOOinl{v_1}{id(T_1)} \approx \vOOinl{v_2}
		: \POOsum{T_1}{T_2}
	}
	\quad
	\inference{
		\hcvOOinl{v_1}{c} \approx v_2
		: \POOsum{T_1}{T_2} &
		c' = seq(c,cast(T_1,l,T_3))
	}{
		\hcvOOinl{v_1}{c'} \approx
		\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
		: \POOsum{T_3}{T_4}	
	}
	\\
	\inference{
	v_1 \approx v_2 : T_2
	}{
	\hcvOOinr{v_1}{id(T_2)} \approx \vOOinr{v_2}
	: \POOsum{T_1}{T_2}
	}
	\quad
	\inference{
	\hcvOOinr{v_1}{c} \approx v_2
	: \POOsum{T_1}{T_2} &
	c' = seq(c,cast(T_2,l,T_4))
	}{
	\hcvOOinr{v_1}{c'} \approx
	\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
	: \POOsum{T_3}{T_4}
	}
	\end{gather}
	\caption{Bisimulation between \effCEK{C} and \ineffCEKD}
	\label{fig:bisim-SC-D}
\end{figure}

Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
introduce one more definition: $s_1 \approx^{*} s_2$ if and only if there 
exists $s_2' \in \text{\ineffCEKD}$
such that $\judgeCreduceTrans{s_2}{s_2'}$ and $s_1 \approx s_2'$.

\todo[inline]{Standardize theorem statement -KC}
\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
	\label{thm:surely-monoidic-reduce}
	For all instance of Cast ADT $C$, 
	if $C$ is \lazyD{} and is a monoid and $cast(T,l,T)=id(T)$,
	$ s_{1}, s_{1}' \in \text{\effCEK{C}}$,
	$ s_{2}, s_{2}' \in \text{\ineffCEKD}$,
	$ s_{1} \approx s_{2}$,
	$ \judgeSreduce{C}{s_{1}}{s_{1}'}$, and
	$ \judgeDreduce{s_{2}}{s_{2}'}$, then
%	then there exist$s_2'' \in \text{\ineffCEKD}$such that
	\[ \exists s_2'' \in \text{\ineffCEKD}: \;
	\judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2'' \]
%	\begin{enumerate}
%		\item if $\judgeDreduce{s_1}{s_3}$,
%		then
%		there exist$s_5 \in \text{\ineffCEKD}$, $s_4 \in \mathcal{S}(C)$,
%		such that \begin{itemize}
%			\item$s_5 \approx s_4$, and
%			\item$\judgeSreduce{C}{s_2}{s_4}$,
%			\item$\judgeDreduceTrans{s_3}{s_5} $
%		\end{itemize}
%		\item if $\judgeSreduce{C}{s_2}{s_4}$,
%		then
%		there exist$s_3 \in \mathcal{C}$,
%		such that \begin{itemize}
%			\item$s_3 \approx s_4 $
%			\item$\judgeDreduceTrans{s_1}{s_3} $
%		\end{itemize}
%	\end{enumerate}

Or diagrammatically, 
\[\begin{array}{clclc}
s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
\rotatebox[origin=c]{90}{$\approx$} 
& & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
s_{2} & 
\longrightarrow_{\text{\ineffCEKD}} & s_2' &
\longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
\end{array}\]

\end{lemma}
\begin{proof}
	By following the transition rule of \ineffCEKD. See the supplementary 
	materials for details.
\end{proof}

\todo[inline]{An extra property is required after changing case to small-step 
-KC}
\begin{proposition}[Correctness of \effCEK{C}]
	\label{thm:surely-monoidic-eval}
	if $\judgetype{\emptyset}{e}{T}$ and $o : T$ and $C$ is a 
	\lazyD{} Cast ADT and a monoid,
	\[
	\text{\evalEqv{\effCEK{C}}{\ineffCEKD}}
	\]
\end{proposition}
\begin{proof}Proving left implies right is trivial.
To prove $\judgeDeval{e}{o}$ implies $\judgeSeval{C}{e}{o}$, 
we firstly take one steps in \effCEK{C}, and catch it up in \ineffCEKD\ by 
taking one or more steps in \ineffCEKD. As we just took a positive number of 
steps, we are closer to the halting state.
\end{proof}

@@

In this subsection, we prove that for all $C$, if $C$ is a Lazy D Cast ADT, 
then \evalEqv{\ineffCEKD}{\effCEK{C}}. We first 
prove that all $S(C)$ where $C$ is a Lazy D Cast ADT are equivalent, then 
connect this theorem to Lemma~\ref{thm:surely-monoidic-eval}.

We prove the equivalence among \effCEK{S(C)} with strong bisimulation. This 
time almost all the bisimulation relations are all derived from definitions 
except the relaton for casts, which is by cast constructors:
\begin{gather*}
\inference{
}{
	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
}
\quad
\inference{
}{
	id_1(T) \approx id_2(T)
}
\quad
\inference{
	c_1 \approx c_2 &
	c_3 \approx c_4
}{
	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
}
\end{gather*}

@@

	Or diagrammatically, 
	\[\begin{array}{clc}
	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
	\rotatebox[origin=c]{90}{$\approx$} 
	& & \rotatebox[origin=c]{90}{$\approx$} \\
	s_{2} & 
	\longrightarrow_{\text{\ineffCEKD}} & s_2' \\
	\end{array}\]
\end{lemma}
\begin{proof} 
	This proof is effectively a duplication of the transition rule of 
	\effCEK{S(C)}.
	The key ideas of this proof are undoing sequencing with the property (2) of 
	Lazy D Cast ADT, and handling all possibly uses of $
	cast(T,l,T)$ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of \lazyD{} Cast ADT]
	\label{thm:surely-lazyD-eqv}
	if $\judgetype{\emptyset}{e}{T}$, $o : T$, and $C_1$ and $C_2$
	are \lazyD\ Cast ADTs,
	\[
	eval_{S(C_1)} = eval_{S(C_2)}
	\]
\end{proposition}
\begin{proof}
	By induction with the help of Lemma~\ref{thm:CEKS-bisim}.
\end{proof}

\begin{theorem}[\lazyD\ Cast ADT Respects \ineffCEKD]
	\label{thm:surely-lazyD-correct}
	if $\judgetype{\emptyset}{e}{T}$ and $o : T$ and $C$ is a 
	\lazyD{} Cast ADT.
	\[
	\text{\evalEqv{\ineffCEKD}{\effCEK{C}}}
	\]
\end{theorem}
\begin{proof}
	If we have a Lazy D Cast ADT and it is a monoid, this 
	proof is immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
	Proposition~\ref{thm:surely-lazyD-eqv}. One such representation is to 
	represent casts as a list of triples of type, label, and type, where 
	$id(T)$ is the empty list and $seq(c,c)$ is the list append. Another such 
	representation is the \lazyD\ hypercoercion!
\end{proof}

>>>>

\todo[inline]{The notation $\hcvOOinj{P}{v}$ is non-standard
   and should be explained. -JS}

@@

\subsection{\effCEK{C} is equivalent to \ineffCEKD{}, provided $C$ is an instance of the Lazy D ADT}
\label{secc:framework:monoid-correct}

In this subsection, we prove that for all $C$, if $C$ is a Lazy D Cast
ADT, then
\[
  \evalEqv{\effCEK{C}}{\ineffCEKD}
\]
The main work of the proof is in a lemma that establishes a weak
bisimulation between \effCEK{C} and \ineffCEKD{}.  The bisimulation
goes more smoothly if we require two more properties of the cast
representation: that the casts form a monoid (the $id$ and $seq$
operators) and that the cast constructor is equivalent to the identity
operator when applied to an identical source and target type.
However, the final theorem does not require these two properties
because we can prove 1) that \effCEK{C_1} and \effCEK{C_2} are
equivalent for any two Lazy D Cast ADTs $C_1$ and $C_2$, and 2) there
is an instance of the Lazy D Cast ADT, named $L$, that is a monoid and
satisfies the two extra properties, and is therefore equivalent to
\ineffCEKD{}. So by transitivity, for any Lazy D Cast ADT $C$ we have
\evalEqv{\effCEK{C}}{\ineffCEKD}.

\subsubsection{Weak Bisimulation between \effCEK{C} and \ineffCEKD{}}

We shall prove that if a instance of Cast ADT $C$ is Lazy D, is a
monoid, and if $cast(T,l,T) = id(T)$, then there is
%% $eval_\mathcal{D} = eval_{\mathcal{S}(C)}$. We proof this lemma with
a weak bisimulation between \effCEK{C} and \ineffCEKD{}.
We define monoid as follows.

\begin{definition}[Monoid]
	A Cast ADT is a monoid if 
	for all
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c_1) = c_1$,
		\item $seq(c_1,id(T_2)) = c_1$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{definition}

@@

\todo[inline]{How does the following bisimulation relation
  compare to the one used in the Blame and Coercion paper?
  Are there any guiding principles to how this bisimulation
  relation was constructed? -JS}

Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation.  It is
the smallest congruence relation that also includes the pairs induced
by the rules in Fig.~\ref{fig:bisim-SC-D}.
%
The relation is mutually defined on continuations, written $\kappa
\approx \kappa$, and values, written $v \approx v : T$, where $T$ is
their type.
%
If $k \approx \kappa$, adding an identity cast on top of $k$ gives a related 
continuation.
%
\todo[inline]{The use of ``wrap'' obscures this explanation.
  Consider getting rid of wrap by inlining it. -JS}
%
If $\kappa_1 \approx \kappa_2$, extending $\kappa_1$ and $\kappa_2$ with the 
same cast gives related results.
%
If two values of type $P$ are related, injecting them to $\TOOdyn$ gives 
related values.
%
% The following is part of being a congruence. -JS
%Unit values are of course related. 
%
To relate to a non-casted function in \ineffCEKD, the function in \effCEK{C} 
must use identities as its casts.
%
If functions are related, we can apply the same cast on both side.
%
Rules for products and sums are similar.

\todo[inline]{Give the motivation for the following lemma. Where
  does it get used? As in, which case of which other lemma or theorem? -JS}

@@

\begin{figure}
	$\text{\effCEK{C}} \approx \text{\ineffCEKD}$
%	\[\dots\]

	\fbox{$\kappa \approx \kappa$}
	\begin{gather*}
	\inference{
		k \approx \kappa
	}{
		wrap(k) \approx \kappa
	}
	\quad
	\inference{
		\kappa_1 \approx \kappa_2
	}{
		ext(cast(T_1,l,T_2),\kappa_1) \approx 
		\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_2}
	}
\\
	\end{gather*}
\\	
	\fbox{$v \approx v : T$}
	\begin{gather*}
	\inference{
		v_1 \approx v_2 : P
	}{
		\hcvOOinj{P}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
		: \TOOdyn
	}
\\ \\
	%% \inference{}{
	%% 	\hcvOOtt \approx \vOOtt : \POOunit
	%% }
	%% \quad
	\inference{}{
		\hcvOOtt \approx \vOOcast{\vOOtt}{\cOOcast{\POOunit}{l}{\POOunit}}
		: \POOunit
	}
	\\ \\
	\inference{
		\rho_1 \approx \rho_2 &
		dom(\rho_1) = dom(\rho_2) = \Gamma \\
		\Gamma , x : T_1 \vdash e : T_2
	}{
		\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)}
		\approx
		\vOOfun{\rho_2}{x}{e}
		: \POOfun{T_1}{T_2}
	}
\\ \\
\inference{
\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v_2 : \POOfun{T_1}{T_2} \\
%		\judgeType{\hcvOOfun{c_1}{\rho}{x}{e}{c_2}}{\POOfun{T_1}{T_2}} \\
c_1' = seq(cast(T_3,l,T_1),c_1) \\
c_2' = seq(c_2,cast(T_2,l,T_4))
}{
\hcvOOfun{c_1'}{\rho}{x}{e}{c_2'}
\approx
\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}}
: \POOfun{T_3}{T_4}
}
\\ \\
	\inference{
		v_1 \approx v_2 : T_1 &
		v_3 \approx v_4 : T_2 &
	}{
		\hcvOOcons{v_1}{id(T_1)}{v_3}{id(T_2)}
		\approx
		\vOOcons{v_2}{v_3}
		: \POOprod{T_1}{T_2}
	}
\\ \\
	\inference{
		\hcvOOcons{v_1}{c_1}{v_3}{c_2} \approx v_2 : \POOsum{T_1}{T_2} \\
		c_1' = seq(c_1,cast(T_1,l,T_3)) \\
		c_2' = seq(c_2,cast(T_2,l,T_4))
	}{
		\hcvOOcons{v_1}{c_1'}{v_3}{c_2'} \approx
		\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{\POOprod{T_3}{T_4}}}
		: \POOprod{T_3}{T_4}
	}
\\ \\
	\inference{
		v_1 \approx v_2 : T_1
	}{
		\hcvOOinl{v_1}{id(T_1)} \approx \vOOinl{v_2}
		: \POOsum{T_1}{T_2}
	}
	\quad
	\inference{
		\hcvOOinl{v_1}{c} \approx v_2
		: \POOsum{T_1}{T_2} &
		c' = seq(c,cast(T_1,l,T_3))
	}{
		\hcvOOinl{v_1}{c'} \approx
		\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
		: \POOsum{T_3}{T_4}	
	}
	\\
	\inference{
	v_1 \approx v_2 : T_2
	}{
	\hcvOOinr{v_1}{id(T_2)} \approx \vOOinr{v_2}
	: \POOsum{T_1}{T_2}
	}
	\quad
	\inference{
	\hcvOOinr{v_1}{c} \approx v_2
	: \POOsum{T_1}{T_2} &
	c' = seq(c,cast(T_2,l,T_4))
	}{
	\hcvOOinr{v_1}{c'} \approx
	\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
	: \POOsum{T_3}{T_4}
	}
	\end{gather*}
	\caption{Bisimulation between \effCEK{C} and \ineffCEKD}
	\label{fig:bisim-SC-D}
\end{figure}

Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
introduce one more definition.

\begin{definition}[$s \approx^{*} s$]
Given any two states $s_1$ and $s_2$, we write $s_1 \approx^{*} s_2$
if and only if there exists a state $s_2' \in \text{\ineffCEKD}$ such
that $\judgeDreduceTrans{s_2}{s_2'}$ and $s_1 \approx s_2'$.
\end{definition}

\todo[inline]{Standardize theorem statement -KC}

\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
  \label{thm:surely-monoidic-reduce}
  Suppose $C$ is an instance of the Cast ADT
  and the \lazyD{} ADT, $C$ is a monoid,
  and $cast(T,l,T)=id(T)$.
  If
  $s_{1}, s_{1}' \in \text{\effCEK{C}}$,
  $s_{2}, s_{2}' \in \text{\ineffCEKD}$,
  $s_{1} \approx s_{2}$,
  $\judgeSreduce{C}{s_{1}}{s_{1}'}$, and
  $\judgeDreduce{s_{2}}{s_{2}'}$, then
  \todo[inline]{The premise $\judgeDreduce{s_{2}}{s_{2}'}$ is
    unusual for a weak bisimulation. Makes me suspicious.
    That is usually in the conclusion. If this is indeed correct,
    then you'll need to justify/explain it. -JS}
  \[
    \exists s_2'' \in \text{\ineffCEKD}: \;
    \judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2''
  \]
  Or diagrammatically, 
  \[
  \begin{array}{clclc}
    s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
    \rotatebox[origin=c]{90}{$\approx$} 
    & & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
    s_{2} & 
    \longrightarrow_{\text{\ineffCEKD}} & s_2' &
    \longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
  \end{array}
  \]
\end{lemma}
\begin{proof}
  By following the transition rule of \ineffCEKD.
  \todo[inline]{What does ``following the transition rules'' mean?
    That's not normal proof jargon. Do you mean case analysis
    on $\judgeSreduce{C}{s_{1}}{s_{1}'}$?
    -JS}
  See the supplementary materials for details.
\end{proof}

\todo[inline]{An extra property is required after changing case to small-step 
  -KC}

\begin{corollary}[Correctness of \effCEK{C}]
  \label{thm:surely-monoidic-eval}
  Suppose $C$ is an instance of the Cast ADT
  and the \lazyD{} ADT, $C$ is a monoid,
  and $cast(T,l,T)=id(T)$.
  If $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
  \[
    \text{\evalEqv{\effCEK{C}}{\ineffCEKD}}
  \]
\end{corollary}
\begin{proof}
  Proving that the left-hand side implies the right-hand side is
  trivial.  To prove $\judgeDeval{e}{o}$ implies
  $\judgeSeval{C}{e}{o}$, we first take one step in \effCEK{C}, and
  catch it up in \ineffCEKD\ by taking one or more steps in
  \ineffCEKD. As we just took a positive number of steps, we are
  closer to the halting state.
\end{proof}

@@

%% In this subsection, we prove that for all $C$, if $C$ is a Lazy D Cast ADT, 
%% then \evalEqv{\ineffCEKD}{\effCEK{C}}. We first 
%% prove that all $S(C)$ where $C$ is a Lazy D Cast ADT are equivalent, then 
%% connect this theorem to Lemma~\ref{thm:surely-monoidic-eval}.

\subsubsection{\effCEK{C_1} and \effCEK{C_2} are equivalence if $C_1$ and $C_2$ are Lazy D}

We prove the equivalence among two \effCEK{C} machines with a strong
bisimulation. This time almost all the bisimulation relations are all
derived from definitions except the relaton for casts, which is by
cast constructors:
\todo[inline]{By ``derived from the definitions'' do you mean
 that it is a congruence? -JS}

\begin{gather*}
\inference{
}{
	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
}
\quad
\inference{
}{
	id_1(T) \approx id_2(T)
}
\quad
\inference{
	c_1 \approx c_2 &
	c_3 \approx c_4
}{
	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
}
\end{gather*}

@@

	Or diagrammatically, 
	\[\begin{array}{clc}
	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
	\rotatebox[origin=c]{90}{$\approx$} 
	& & \rotatebox[origin=c]{90}{$\approx$} \\
	s_{2} & 
	\longrightarrow_{\text{\ineffCEKD}} & s_2' \\
	\end{array}\]
\end{lemma}
\begin{proof} 
  This proof is effectively a duplication of the transition rule of
  \effCEK{S(C)}.
%
  \todo[inline]{The above sentence is not normal proof jargon.  Are
    you doing a proof by cases on $s_{1}
    \longrightarrow_{\text{\effCEK{C}}} s_1'$? -JS}
%
  The key ideas of this proof are undoing sequencing with the property
  (2) of Lazy D Cast ADT, and handling all possibly uses of
  $cast(T,l,T)$ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of two \lazyD{} Cast ADTs]
  \label{thm:surely-lazyD-eqv}
  Suppose $C_1$ and $C_2$ are \lazyD\ Cast ADTs.
  If $\judgetype{\emptyset}{e}{T}$, $o : T$, then
  \[
  eval_{S(C_1)} = eval_{S(C_2)}.
  \]
\end{proposition}
\begin{proof}
  By induction with the help of Lemma~\ref{thm:CEKS-bisim}.
  \todo[inline]{Induction on what? -JS}
\end{proof}

\begin{theorem}[\lazyD\ Cast ADT Respects \ineffCEKD]
  \label{thm:surely-lazyD-correct}
  Suppose $C$ is a \lazyD{} Cast ADT.  If
  $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
  \[
  \text{\evalEqv{\ineffCEKD}{\effCEK{C}}}
  \]
\end{theorem}
\begin{proof}
	If we have a Lazy D Cast ADT and it is a monoid, this 
	proof is immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
	Proposition~\ref{thm:surely-lazyD-eqv}. One such representation is to 
	represent casts as a list of triples of type, label, and type, where 
	$id(T)$ is the empty list and $seq(c,c)$ is the list append. Another such 
	representation is the \lazyD\ hypercoercion!
\end{proof}
